\documentclass[10pt,a4paper]{report}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Michael C. Kunkel}
\begin{document}
	In ''Introduction``
	\begin{itemize}
		\item For figure 1, it is not clear if the plot shown is for general Dalitz plot, simulated or data corrected. Please define.
		\item Spell check shows multiple errors.
		\item Text shows that you refer to Equation 7, fix this.
		\item The Dalitz plot parameters you list are for the $\eta'$ decays. This should be noted.
		\item explain more how the DP is important to physics.
	\end{itemize}
	In ''G12 Data Set``
	\begin{itemize}
		\item The g12 experiment was a fixed target experiment which ran during March - June 2008 with $26 x 10^{9}$ recorded production triggers ~\cite{G12_AN}.  The experiment, has an energy of the photon beam ranging from 1.142 GeV to  5.425 GeV. However, the threshold production of $\eta^{\prime}$ meson is 1.455 GeV and hence the analysis will report the parameters from the threshold to the maximum available energy. The analysis starts with well calibrated data in ''.root`` format with all events arranged as per the Run number, Event number and PID along with all other informations recorded by the experiment. The final state particles proton, $\pi^{+}$ and $\pi^{-}$ information were extracted from the PART BOS bank and identified using particle identification codes compiled in the ``clas6-trunk" under the package CLASEVENT . The skim were so selected that all events has only one proton, $\pi^{+}$ and $\pi^{-}$ and any number of neutral particles. 
		The complete reaction under study is `` $\gamma$ p $\rightarrow$ $\eta^{\prime}$($\rightarrow$ $\eta$ $\pi^{+}$ $\pi^{-}$) p " and the $\eta$ meson is reconstructed via the missing mass technique. 
		\item Do not need the table, as this is in the g12 analysis note.
		\item In ''Simulation``
	\begin{itemize}
		\item PLUTO++ is the event generator used for this analysis. 
		\item Cite PLUTO++
		\item Spell check shows multiple problems with this subsection
		\item Hadron Physics $\rightarrow$ hadron physics : because neither is s proper noun.
		\item ''obtain outputs in any desired format`` this is ambiguous and not true.
		\item Do not need to itemize your list of simulation chain as this is in the g12 analysis note.
	\end{itemize}
	\end{itemize}		
	In ''Event Selection``
	\begin{itemize}
		\item Do not list the G12 corrections as they are listed on the cover page for all g12 analysis notes. See Checklist on the g12 wiki.
		\item Use the FloatBarrier flag to keep figures where you need them.
		\item More justification for cuts are needed
	\end{itemize}
	In ''Result``
	Will do after I see more in previous sections
\end{document}